Simulations of Ballot Polling Risk-Limiting Audits

### 2022-10-12 providence/sections/pilot.tex
more

Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$ in the simulations. The vertical line denotes the stopping probability of the first round size chosen in the pilot of $140$ ballots. The average number of ballots for such a high stopping probability round schedule is high. blah blah based on plot and some numbers illustrating that point... Of course, average number of ballots is not the only metric that matters when planning an audit.

>>>>

Figure~\ref{fig:pilot_sims} shows the average number of ballots sampled for each value of $p$ in the simulations. The vertical line denotes the stopping probability of the first round size chosen in the pilot of $140$ ballots. The average number of ballots for such a high stopping probability round schedule is high. For the first round size used in the pilot there was an approximately $95\%$ probability of stopping, and consequently in Figure~\ref{fig:pilot_sims}, this corresponds to a higher average total ballots sampled than lower values of $p$. Of course, average number of ballots is not the only metric that matters when planning an audit.
